\chapter{Algebraic topology}
    \begin{abstract}
        
    \end{abstract}
    
    \minitoc
    
    \section{Condensed mathematics} \label{section: condensed_mathematics}
        \subsection{Abelian categories of condensed objects}
            \begin{definition}[Condensation] \label{def: condensation}
                Let $\kappa$ be a fixed regular cardinal and let $\C$ be a hypercomplete $\infty$-category with enough $\kappa$-small limits and enough $\kappa$-small filtered colimits. We then define so-called \textbf{condensed objects} of $\C$ to be $\C$-valued sheaves over the $\kappa$-pro-\'etale site of a point (see proposition \ref{prop: perfect_pro_etale_sites} along with remarks \ref{remark: non_affine_perfect_pro_etale_sites} and \ref{remark: non_perfect_pro_etale_sites} for the notion of pro-\'etale sites).  
                
                Clearly condensed objects of a given $\infty$-category $\C$ satisfying the above conditions form a category. We shall denote it by $\C_{\bullet}$.
            \end{definition}
            \begin{example}
                \noindent
                \begin{itemize}
                    \item \textbf{(Condensed sets):} The pro-\'etale topos $*_{\proet}$ over a point is, by definition, the category of sheaves of sets on the pro-\'etale site of a point. Therefore, this topos is the category of \textbf{condensed sets}.
                    \item \textbf{(Condensed abelian groups and modules):} If $R$ is a condensed commutative ring, then the category ${}_R\Mod_{\bullet}$ of condensed $R$-modules is a \href{https://ncatlab.org/nlab/show/Grothendieck+category}{\underline{Grothendieck category}}; on the other hand, topological abelian groups even fails to form an abelian category, and as we well know: no abelian categories means no homological algebra. This is a biggy, so we shall bestow upon it the dignity of theoremhood (see theorem \ref{theorem: abelian_categories_of_condensed_modules}).
                \end{itemize}
            \end{example}
            \begin{remark}[Condensation and profiniteness] \label{remark: condensation_and_profiniteness}
                Fix a regular cardinal $\kappa$. The $\kappa$-pro-\'etale site of a point is equivalent to the category $\Pro_{\kappa}(\Sets^{\fin})$ of $\kappa$-profinite sets equipped with the coverage generated by jointly surjective finite families of surjective functions. 
            \end{remark}
            
            \begin{definition}[Extremely disconnected sets] \label{def: extrememly_disconnected_sets}
                A compact Hausdorff space $S$ is extremely disconnected if and only if any epimorphism $e: S' \to S$ splits/admits a left-section $s: S \to S'$ (which by definition, satisfies $e \circ s = \id_S$).  
            \end{definition}
            \begin{example}
                \noindent
                \begin{enumerate}
                    \item \textbf{(Stone-\v{C}ech compactifications):}
                    \item \textbf{(A counter-example: the $p$-adics):}
                \end{enumerate}
            \end{example}
            
            \begin{lemma}[Condensed sets and extremely disconnected sets] \label{lemma: condensed_sets_and_extremely_disconnected_sets}
                Fix a regular cardinal $\kappa$. 
                \begin{enumerate}
                    \item 
                    \item 
                \end{enumerate}
            \end{lemma}
                \begin{proof}
                    
                \end{proof}
            
            \begin{theorem}[Abelian categories of condensed modules] \label{theorem: abelian_categories_of_condensed_modules}
                Fix a regular cardinal $\kappa$. Categories of modules ${}_R\Mod_{\bullet}$ over $\kappa$-condensed commutative rings $R$ satisfy the following Grothendieck homological axioms:
                    \begin{enumerate}
                        \item They are abelian categories.
                        \item \textbf{($AB3$ \& $AB3^*$):} They are $\kappa$-small complete and $\kappa$-small cocomplete.
                        \item \textbf{($AB3$ \& $AB4^*$):} Coproducts of monics remain monic, and dually, products of epics remain epic.
                        \item \textbf{($AB5$):} Filtered colimits of exact sequences remain exact. Furthermore, categories of condensed modules are compactly generated: this is to say, its generator, call it $\Lambda$ is a compact object (i.e. the copresheaf ${}_R\Mod_{\bullet}(\Lambda, -)$ preserves filtered colimits).
                        \item \textbf{($AB6$):} $\kappa$-small products commute with $\kappa$-small filtered colimits.
                    \end{enumerate}
            \end{theorem}
                \begin{proof}
                    \noindent
                    \begin{enumerate}
                        \item Categories of condensed modules are categories of internal modules - specifically to the pro-\'etale topos over a point - and so are trivially abelian. 
                        \item \textbf{($AB3$ \& $AB3^*$):} Again, condensed modules are internal modules, and thus the categories they form are \textit{a priori} $AB5$, and hence $AB3$.
                        \item \textbf{($AB4$ \& $AB4^*$):} 
                        \item \textbf{($AB5$):} We have already shown that categories of condensed modules are $AB5$, so it remains to show that the generator of ${}_R\Mod_{\bullet}$ is compact.
                        \item \textbf{($AB6$):} 
                    \end{enumerate}
                \end{proof}
            \begin{corollary}[Properties of categories of condensed modules] \label{coro: condensed_modules_properties}
                By virtue of being a Grothendieck category (i.e. an $AB5$-category with a generator), any condensed module ${}_R\Mod_{\bullet}$ enjoy the following properties:
                    \begin{enumerate}
                        \item 
                            \begin{enumerate}
                                \item If a presheaf $F: {}_R\Mod_{\bullet}^{\op} \to \Sets$ preserves $\kappa$-small limits, then it is representable (i.e. the Yoneda embedding on ${}_R\Mod_{\bullet}$ preserves all $\kappa$-small limits, not just the finite ones).
                                \item If a presheaf ${}_R\Mod_{\bullet}^{\op} \to \Sets$ commutes with all $\kappa$-small colimits, then it possesses a right-adjoint. 
                            \end{enumerate}
                        \item By the \href{https://ncatlab.org/nlab/show/Gabriel-Popescu+theorem}{\underline{Gabriel-Popescu Theorem}}, we can realise ${}_R\Mod_{\bullet}$ as a reflective localisation of some category of modules over a commutative ring. 
                        \item ${}_R\Mod_{\bullet}$ is presentable. 
                    \end{enumerate}
            \end{corollary}
        
        \subsection{Solidity}